---
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
#    template: ./resources/aog-latex-ms.tex
  word_document:
    reference_docx: ./resources/aog_word_style.docx
#fontfamily: mathpazo
fontsize: 11pt
anonymous: false
endnotes: false
pagenumber: 1
bibliography: ../project.bib
biblio-style: ./resources/ajs.bst
title: "Outcomes of Formal Sexual Harassment Complaints in the Federal Workplace"
author:
- affiliation: University of Oregon, Sociology
  name: Emily Beecher
- affiliation: Some Research University
  name: My co-author
keywords: keywords
thanks: Thanks to Aaron Gullickson for not failing me in this course and supporting me in my struggles with this data set. I promise I will try a quant project sometime in the future. I am determined not to let this be the end.
abstract: This is a test abstract.
---
```{r setup, message=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("../../analysis/output/data.RData")
library(ggplot2)
library(readr)
library(texreg)
library(tinytex)
```


# Introduction

In the wake of the #MeToo movement, a lot of awareness of sexual assault and harassment was raised with little tangible recourse or interventions made. Since the nature of a majority of the claims made about sexual harassment and sexual violence occurred within the workplace, a common solution posed by activists, especially socialist feminist activists, has been to unionize the workplace instead of focusing on other methods to curb sexual harassment and sexual violence. Given the lengthy documentation of unions being masculine environments with ugly histories of handling sexual harassment/sexual violence, many are skeptical that only advocating for greater union representation will solve the pervasive problem of sexual assualt and harassment in the workplace. Furthermore, just as present in the national conversation around the #MeToo movement are calls to victims to speak out and report the people that harassed or assaulted them. The literature on sexual violence has explored many reasons why survivors don't report their assaults, including shame, embarassment, fear of repercussions, etc. This paper seeks to build upon that data to explore the types of outcomes that are achieved after filing a formal complaint against someone for sexual harassment or assault in the federal, unionized, workfoce.

# Data and Methods

I use a data from a survey conducted by the United States Merit Protection Board to look at the relationship between reports made to union representatives, coworkers, and management to the rate of negative outcomes in instances of sexual harassment and assault in the federal workplace. The study, titled "Sexual Harassment in the Federal Workplace" (SHFW) was issued three times with different questions to the same sample population; the first survey went out in 1980, the second in 1987, and again in 1994. This study was conducted in direct response to a congressional mandate to the Office of Personnel Management (OPM) to investigate the prevalence of sexual assault and harassment in the federal workplace, specifically among those working within the executive branch of the government.

With use of the OPM's Central Personnel Data File, a disproportionately stratified random sample was compiled consisting of federal employees in the executive branch. It was stratified by sex, race, salary, and organization. The 1994 survey, the data of which is analyzed in this paper, went out by mail to the homes of about 10,000 federal workers based in Washington D.C. The survey was returned at a 85% completion rate, meaning that around 8,500 surveys were returned. Respondents were asked to recall incidences of sexual assault and harassment that occurred in the previous two years (May 1992-May 1994). The previous two surveys were also sent by mail to the sample, providing researchers with longitudinal data regarding sexual harassment in the workplace.

The main dependent variable in this study is "bad outcome" - how the respondent's life was impacted by both the instance of sexual harassment and filing the formal complaint, if they filed one. "Bad outcome" was operationalized using one question on the main survey that asked respondents if they had a) experienced worsening conditions at work, b) been transferred, c) got a bad reference or were denied a promotion, d) been fired, or e) felt they had no other choice but to quit their job. The formal complaints that respondents were asked about included a) internal investigations, b) external investigations, c) union grievances, d) EEO investigations, and e) "other" investigations. No one in the 1994 sample initiated an interal investigation. See limitaitons for a further discussion of the formal complaint breakdown.

# Results

I narrowed my overall sample down to just the people that experienced an instance of sexual assault or harassment, liminiting my sample population down to just 282 people. See the limitations section for further discussion of the problems of a small sample size.
After narrowing my sample to just the individuals that experienced an instance of sexual assault or harassment in the workplace, I analyzed the data to determine the outcomes that these individuals achieved and how the outcome they experienced is associated with whether or not they filed a formal complaint. My analysis shows that people who did not file a formal complaint were 87.5% more likely to experience a neutral or positive outcome. Conversely, if someone filed a formal complaint, they only had a 5% chance of experiencing a positive outcome. This relationship is demonstrated in Figure 1 (the exact numerical breakdown is 247/282 people with instances of sexual harassment did not file a complaint and did not have a negative outcome; 8 people suffered a negative outcome and did not file a complaint; 15 people filed a complaint and didn't expereince a negative outcome; and 12 people filed a complaint and experienced a negative outcome). 
Generally, people were unlikely to file a grievance with their union - 8% of people filed complaints in response to sexual harassment and 1.7% of people filed grievances specifically (see: limitations) - but when they did, they were less likely to receive a positive outcome.

```{r figure1, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(sexharass, aes(x=bad_outcome_fctr, y=..prop.., group=1))+
  geom_bar()+
  facet_wrap(~file_complaint_fctr)+
  scale_y_continuous(labels=scales::percent)+
  labs(x="Instance of sexual harassment: outcome", y=NULL, 
       title="Effect of formal complaints on bad outcomes: sexual 
       harassment")+
  theme_bw()
```

```{r models,echo=FALSE, warning=FALSE, message=FALSE}
model1 <- glm(bad_outcome~file_complaint, data=sexharass)
model2 <- glm(bad_outcome~file_complaint+grievance, data=sexharass)
model3 <- glm(bad_outcome~outsideinvest, data=sexharass)
model4 <- glm(bad_outcome~file_complaint+grievance+outsideinvest, data=sexharass)
texreg(list(model1, model2, model3, model4),
       custom.coef.names = c("Intercept", "complaint filed", "filed grievance", "outside investigation"),
       caption="Regression models predicting a bad outcome to an instance of sexual harassment",
       caption.above = TRUE)
```

The models above further explore the relationship between negative outcomes and filing a formal complaint in response to an instance of sexual harassment or assault. As all models indicate that whether or not the survivor filed a complaint is the most significant factor determining the quality of the outcome. Filing a complaint meant that people were 1.5 times more likely to suffer a negative outcome and, when holding the type of complaint constant, people were stll about 1.5 times more likely to suffer a negative outcome when experiencing sexual harassment at work. Models 3 and 4 show a significant effect that filing report that spurs on an outside investigation has on the likelihood of experiencing a bad outcome - people who file a report for an outside investigation are about 2 times more likely to suffer negative consequences (see: limitations).

# Conclusions
Filing formal reports when experiencing sexual assault or harassment at work does not appear to make the situation any better - in fact, formal reports are associated with a higher frequency of negative outcomes. These findings could indicate that, not only does filing a grievance with the representative union not make a significant difference, but survivors of harassment may be better off not filing formal reports at all. However, there are significant limitations both to this dataset an in the interpretation of these conclusions that should be addressed.

#Limitations
Admittedly, this is not a great project, because the data gathered had significant limitations.
First, the 1994 survey only went out to 8,000 people, and only 282 of those people had an incident happen to them at work. This limits the generalizability of the data and constricts further subsets of the data signficantly. For instance, only 27 people filed a formal complaint: 4 of those an outside investigation, 5 of those a grievance, 8 of those an EEO investigation, 4 that filed an "other" investigation, 6 that did not specify, and none of those an internal investigation. Only 20 people reported that they experienced a bad outcome because of this situation. That is hardly any data from which to draw conclusions.

Secondly, there might be other reasons or spurious variables to explain why the respondent faced bad outcomes that might not have anything to do with the complaint filed. The survey was not formatted in such a way that respondents could effectively signify that their working conditions got worse because of either the harassment itself OR the complaint that was filed. And ultimately, they may be too wound up in the same circumstance to be separated from each other in any meaningful way. A larger data set might be able to break it down enough to make these patterns clearer.

Finally, if I was going to do this project again (with better data), I might look at how their surpervisor/union rep/etc. responded to the report of sexual harassment in conjunction with the experienced outcome to better answer the more specific question about whether reporting to the union was better than anything else. I would also include other kinds of responses in my analysis, like confrontation, avoidance, or telling a coworker, to assess how bad (or helpful) filing formal complaints are. Lastly, I'd control for age, education, and degree of influence (measured by how long they've been working in their job). With a larger data set, this should make the patterns clearer and begin to separate the act of filing a complaint from the harassment itself.

# References
