---
title: "Analysis for Project"
output: 
  html_document: 
    fig_height: 6
    fig_width: 9
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("useful_functions.R")
load("output/data.RData")
library(ggplot2)
library(scales)
library(ggalt)
library(ggrepel)
library(readr)
library(texreg)
library(stargazer)
```

# Introduction
<a href="#top">Back to top</a>

Use this R Markdown to perform the main analysis for the project. I use this basically as a lab notebook. It contains the main analysis and a variety of sensitivity analysis. The code in this documents serves as a baseline for the eventual tables and figures that will go into the paper. At the same time it will serve as a record of all supplementary analyses performed. 

```{r figure1, echo=FALSE, message=FALSE}
ggplot(sexharass, aes(x=bad_outcome, y=..prop.., group=1))+
  geom_bar()+
  facet_wrap(~file_complaint)+
  scale_y_continuous(labels=scales::percent)+
  labs(x="Instance of sexual harassment: outcome", y=NULL, 
       title="Effect of formal complaints on bad outcomes: sexual harassment")+
  theme_bw()
```


```{r models, results="asis"", message=FALSE}
model1 <- glm(bad_outcome~file_complaint, data=sexharass)
model2 <- glm(bad_outcome~file_complaint+grievance, data=sexharass)
model3 <- glm(bad_outcome~file_complaint+outsideinvest, data=sexharass)
model4 <- glm(bad_outcome~file_complaint+grievance+outsideinvest, data=sexharass)
screenreg(list(model1, model2, model3, model4),
       custom.coef.names = c("Intercept", "complaint filed", "filed grievance", "outside investigation"),
       caption="Regression models predicting a bad outcome to an instance of sexual harassment",
       caption.above = TRUE)
```

```{r models, results="asis"", message=FALSE}
model1 <- glm(bad_outcome~file_complaint, data=sexharass)
model2 <- glm(bad_outcome~grievance, data=sexharass)
model3 <- glm(bad_outcome~outsideinvest, data=sexharass)
model4 <- glm(bad_outcome~file_complaint+outsideinvest, data=sexharass)
model5 <- glm(bad_outcome~file_complaint+grievance, data=sexharass)
model6 <- glm(bad_outcome~file_complaint+grievance+outsideinvest, data=sexharass)
model7 <- glm(bad_outcome~sex, data=sexharass)
model8 <- glm(bad_outcome~file_complaint+sex, data=sexharass)
screenreg(list(model1, model2, model3, model4, model5, model6, model7, model8),
       custom.coef.names = c("Intercept", "complaint filed", "filed grievance", "outside investigation", "sex"),
       caption="Regression models predicting a bad outcome to an instance of sexual harassment",
       caption.above = TRUE)
```


